### 2019-02-04 thesis_report/introduction.tex
remove output ipynb

	\comment{What are Majorana bound states}
	Majorana particles are particles that always come in pairs: one pair of Majorana's forms a single electronic state.
	Disambiguating electrons and holes into their Majorana counterparts is often analogized with splitting a complex number into its real and imaginary part.
	We write the Majorana operators in terms of the creation(annihilation) and annihilation(creation) operators of electrons(holes), respectively $\hat{c}^\dagger$ and $\hat{c}$:

@@

	Inverting this, we get,
	\begin{align}
		\gamma_1 = \hat{c} + \hat{c}^\dagger && \gamma_2 = i \left( \hat{c} - \hat{c}^\dagger \right)
		\label{eq:intro_maj2ferm}
	\end{align}

	Note that the basic excitation is still a fermion (electron/hole); one cannot have just one Majorana, they always come in pairs.
	The idea is to create a system where we have a single pair of Majoranas which is seperated in space.

	A system in which this seperation can be accomplished was first proposed by Kitaev~\cite{kitaev_unpaired_2001}.
	We consider a one dimensional chain of sites which can host a single fermion, and thus a pair of Majoranas.
	Suppose that the occupation of a site by a fermion comes at the cost of energy $\mu$.
	Also, we consider the situation where there is an interaction energy between neighboring sites: $t$ quantifies the energy cost of one site being occupied while the adjacent isn't, and $\Delta$ is the gain in energy if adjacent sites are both occupied or empty.
	This leads to the following Hamiltonian:

@@

	Considering equation \eqref{eq:intro_ferm2maj} we can also write the Hamiltonian above using Majorana operators.
	In this way, we get a Hamiltonian describing pairing energies between Majoranas on adjacent sites.
	In figure, we discern two extremes, one is the situation where the pairing energy is minimal for Majorana pairs on the same site:
	\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.95\columnwidth]{images/majorana_trivial_pairing}
	\caption{Trivial Majorana pairing in a Kitaev chain}
	\label{fig:trivial_majoranas}
	\end{figure}

@@

	As is apparent from the above image, this would leave two unpaired Majoranas at the ends of the chain.
	This is the state we are interested in: the Majorana state, where two Majoranas are seperated in space.
	This physical seperation has the effect of not allowing simple local perturbations to disturb the system, thus inherently protecting the system against decoherence.

>>>>

	\comment{What are Majorana bound states}
	Majorana particles are particles that always come in pairs: one pair of Majorana's forms a single electronic state.
	Disambiguating electrons and holes into their Majorana counterparts is analogous to splitting a complex number into its real and imaginary part.
	We write the Majorana operators in terms of the creation (annihilation) and annihilation (creation) operators of electrons (holes), respectively $\hat{c}^\dagger$ and $\hat{c}$:

@@

	Inverting this, we obtain,
	\begin{align}
		\gamma_1 = \hat{c} + \hat{c}^\dagger && \gamma_2 = i \left( \hat{c} - \hat{c}^\dagger \right)
		\label{eq:intro_maj2ferm}
	\end{align}

	Note that the basic excitation is still a fermion (electron/hole); one cannot have just one Majorana, they always come in pairs.
	The idea is to create a system where we have a single pair of Majoranas which is separated in space.

	A system in which this separation can be accomplished was first proposed by Kitaev~\cite{kitaev_unpaired_2001}.
	We consider a one dimensional chain of sites which can host a single fermion, and thus a pair of Majoranas.
	Suppose that the occupation of a site by a fermion comes at the cost of energy $\mu$.
	Also, we consider the situation where there is an interaction energy between neighboring sites: $t$ quantifies the energy cost of one site being occupied while the adjacent is not, and $\Delta$ is the gain in energy if adjacent sites are both occupied or empty.
	This leads to the following Hamiltonian:

@@

	Considering equation \eqref{eq:intro_ferm2maj} we can also write the Hamiltonian above using Majorana operators.
	In this way, we get a Hamiltonian describing pairing energies between Majoranas on adjacent sites.
	We discern two extremes: In figure \ref{fig:trivial_majoranas}, the situation where the pairing energy is minimal for Majorana pairs on the same site:
	\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.95\columnwidth]{images/majorana_trivial_pairing}
	\caption{Trivial Majorana pairing in a Kitaev chain}
	\label{fig:trivial_majoranas}
	\end{figure}

@@

	As is apparent from the above image, this would leave two unpaired Majoranas at the ends of the chain.
	This is the state we are interested in: the Majorana state, where two Majoranas are separated in space.
	This physical separation has the effect of not allowing simple local perturbations to disturb the system, thus inherently protecting the system against decoherence.
